Efficient simulation of individual-based population models

### 2024-10-11 article.qmd
computo second review

>>>>

It can be noted that under appropriate rescaling and when the population size goes to infinity, an IBM can be approximated by a non linear transport PDE, structured by age and trait. A central limit theorem can also be obtained under appropriate assumptions [@tran_2008]. In the presence of interactions as in @sec-example-interaction for instance, the IBM goes almost surely to extinction in finite time, which is not the case for the limit PDE. In this case, simulating the microscopic process can be quite useful for approximating the distribution of the extinction time. Other applications of IBM simulations can include the simulation of multiscale population evolution, strongly heterogeneous populations, or small populations with strong interactions.
